Labor Markets and Technological Change: Evidence from Electronic Health Records

### 2022-04-18 Paper/Paper.tex
Updates from Overleaf

The effect of EHR exposure on patient count is shown in Figure \ref{fig:patient}. For physicians of any age, patient count increases by 11.5 patients in the year of EHR exposure, 24 patients in the year after exposure, 15.3 patients in the second year after exposure, and then no effect after the second year. These results translate to a .5-1\% increase in the number of patients seen relative to the mean. As with other outcomes, this result is totally due to changes by the younger group of physicians. While there is a statistically larger effect for younger physicians relative to senior physicians (who likely take longer to adapt to technology changes), the observed effect is economically trivial.

Since this is a demand-driven variable as well, I investigate whether any external factors may shift the demand for health care over the sample period.

@@

@@

\begin{figure}
    \centering
    \caption{Hospital EHR Adoption Over Time}
    \includegraphics[scale=.6]{Objects/hosp_treat.png}
    \label{fig:hosp_treat}
\end{figure}

@@

>>>>

The effect of EHR exposure on patient count is shown in Figure \ref{fig:patient}. For physicians of any age, patient count increases by 11.5 patients in the year of EHR exposure, 24 patients in the year after exposure, 15.3 patients in the second year after exposure, and then no effect after the second year. These results translate to a .5-1\% increase in the number of patients seen relative to the mean. As with other outcomes, this result is totally due to changes by the younger group of physicians. While there is a statistically larger effect for younger physicians relative to senior physicians (who likely take longer to adapt to technology changes), the observed effect is not largely meaningful.

Since this is also a demand-driven variable as well, I investigate whether any external factors may shift the demand for health care over the sample period.

@@

However, these results include physicians who shift place of work, which may lead to biased estimates since a physician could switch hospitals due to an EHR and then change practice behavior due to the move, not due to the EHR. Thus, I limit the sample to only physicians who work stay with the same one hospital through the entire sample. These physicians do not retire or see patients in another hospital. Thus, when an EHR is implemented, the physician remains utilizing the EHR for the remainder of the period. I present the results for this limited sample in Figure \ref{fig:limi}.

@@

\begin{figure}
    \centering
    \caption{Hospital EHR Adoption Over Time}
    \includegraphics[scale=.8]{Objects/hosp_treat.pdf}
    \label{fig:hosp_treat}
\end{figure}

@@

\begin{figure}[p]
    \centering
    \caption{Effect of EHR Exposure on Patient Count, Limited Sample}
    \includegraphics[scale=.4]{Objects/patient2_plot.pdf}
    \label{fig:patient2}
\end{figure}
